
\chapter{Existing Solutions}
\section{Evaluation of Existing Solutions}
Six different web solutions addressing fall risk prevention were evaluated according to set criteria based on the functional requirements of the project. Positive and negative aspects of the individual cites were summarized.

\subsection{Evaluation Criteria}
 The first method of evaluation included a brief overview of initial impressions of the existing solutions. Several aspects of the sites were sorted into pros and cons relating to how well the sites would solve our customer's problem.
 
 The second method of evaluation is a formal evaluation of the sites based on a selection of the functional requirements, see Table  \ref{table:evaluationMatrix}. Here, we compared the solutions to a selection of the  functional requirements we decided were the most characteristic of a fitting solution:
\\

F1: Register user profile

F4: Log in functionality for users 

F6: Invite friends to events 

F9: View personal fitness information

F13: Add friends to personal network

F15: Download app(s)

F16: View exercises

F17: Take a fitness test

F19: Basic information about fall risk\\
\\
(For a full description of functional requirements see Table \ref{table:funcReq})

\subsection{Ncoa.org/falls-prevention/}
This is a national fall prevention-program spread among states of the US. NCOA is partnering with nonprofit organisations, government, and business to improve the health and economic to 10 million older adults by 2020.
\begin{table}[H]
\begin{center}
\begin{tabu} to 0.8\textwidth{ |X[l]|X[l]| } 
\hline \rowcolor{lightgray}
Pros & Cons \\
\hline
A lot of fall prevention tips for older adult and caregivers & NCOA uses fall statistics to motivate older adults and caregiver. Our customer have bad experience with this kind of motivation.

 \\ 
\hline
Falls prevention programs that have been proven to help elders reduce their risk for falling & This site is not a service. It's only a information site that makes the public aware of which services that exists in the US.

\\ 
\hline
\end{tabu}
\end{center}
\caption{Evaluation of Ncoa.org}
\end{table}

\subsection{Endomondo.com}
This is a personal trainer app. It's almost a free app and website that should make fitness fun and helps you stay motivated. If your are premium member you will have access to the full service.
\begin{table}[H]
\begin{center}
\begin{tabu} to 0.8\textwidth{ |X[l]|X[l]| } 
\hline \rowcolor{lightgray}
Pros & Cons \\
\hline
Very similar to our concept, and great GUI & Service related to young audience 

\\ 
\hline
Collect GPS-data with app & All users can see your workout data 

\\ 
\hline
\end{tabu}
\end{center}
\caption{Evaluation of Endomondo.com}
\end{table}

\subsection{Fallforebygging.no}
Fallforebygging.no \cite{fallforebygging} is a Norwegian website dedicated to preventing falls. It is an extensive website with content ranging from causes and consequences to  prevention methods, and includes videos, information about lectures and links to more information. 
\begin{table}[H]
\begin{center}
\begin{tabu} to 0.8\textwidth{ |X[l]|X[l]| } 
\hline \rowcolor{lightgray}
Pros & Cons \\
\hline
Include much statistics about fall risk & 
The website has a image of a fall on the main page. Our customer clearly wants us to not feed into the stigmas regarding old age and health 

\\ 
\hline
Specific section on causes and methods of prevention & Negative statistics \\ 
\hline
\end{tabu}
\end{center}
\caption{Evaluation of Fallforebyggin.no}
\end{table}

\subsection{Stopfalls.org}
This is the website of Fall Prevention Center of Excellence based in California. Their mission is  “[...] to provide leadership, create new knowledge, and develop sustainable programs for seniors and their families, professionals, program administrators, and policymakers.” \cite{stopfalls}


\begin{table}[H]
\begin{center}
\begin{tabu} to 0.8\textwidth{ |X[l]|X[l]| } 
\hline \rowcolor{lightgray}
Pros & Cons \\
\hline
While not free, the site offers brochures with exercise programs to prevent falls. They appear inspiring and include positive and supporting images. & 
The geographical connection of the site is unsuitable for our purposes. It offers link to several California based services, which naturally are of no importance to Norwegian seniors.  

\\ 
\hline
The site has a purchasable DVD with more exercises one can do at home to prevent falls.
 & The language of the site of naturally an obstacle, but the development team can nonetheless  use the site as inspiration. 
 
 \\ 
\hline
\end{tabu}
\end{center}
\caption{Evaluation of Stopfalls.org}
\end{table}

\subsection{Dytt.no}
\begin{table}[H]
\begin{center}
\begin{tabu} to 0.8\textwidth{ |X[l]|X[l]| } 
\hline \rowcolor{lightgray}
Pros & Cons \\
\hline
The activities fit everyone and they are easy &
The service focuses on businesses, not private persons \\ 
\hline
Provides health benefits & The service is not free \\ 
\hline
\end{tabu}
\end{center}
\caption{Evaluation of Dytt.no}
\end{table}

\subsection{Facebook.com}
This is a social networking site where users can grow their network by becoming friends with other users. Once a user, one can create events and groups and invite friends to join them. Users are also provided with a newsfeed of what is going on in their network. 
\begin{table}[H]
\begin{center}
\begin{tabu} to 0.8\textwidth{ |X[l]|X[l]| } 
\hline \rowcolor{lightgray}
Pros & Cons \\
\hline
Social network allowing users to create events and receive information of what others in their network are doing &
No focus on fitness \\ 
\hline
\end{tabu}
\end{center}
\caption{Evaluation of Facebook.com}
\end{table}

\subsection{Summary}
Table \ref{table:evaluationMatrix} sums up which functional requirements are fulfilled by the six websites evaluated above. 

\begin{table} [!h] 
    \begin{tabular}{@{} cl*{10}c @{}}
        & & \multicolumn{10}{c}{Websites} \\[2ex]
        & & \rot{NCOA.org} & \rot{Endomondo.com} & \rot{Fallforebygging.no} & \rot{Stopfalls.org} 
        & \rot{Dytt.no}  & \rot{Facebook.com} \\
        \cmidrule{2-9}
        & F1              &     & \OK &     &     & \OK &  \OK\\
        & F4              &     & \OK &     &     & \OK &  \OK\\
        & F6              &     & \OK &     &     & \OK &  \OK\\
        & F9              &     & \OK &     &     & \OK &     \\
        & F13             &     & \OK &     &     & ?   &  \OK\\
        & F15             &     & \OK & \OK &     &     &  \OK\\
        & F16             & \OK & \OK &     & \OK &     &     \\
        & F17             &     &     &     &     &     &     \\
        & F19             & \OK &     & \OK & \OK &     &     \\
 \rotvert{\rlap{~Functional Requirements}}
        & Comments                &  &   &   &   &   &   &    \\
        \cmidrule[1pt]{2-9}
    \end{tabular}
    \caption{Evaluation of Existing Solutions}
    \label{table:evaluationMatrix}
\end{table}

Based on Table \ref{table:evaluationMatrix}, we will get inpiration form Dytt.no, Endomondo.com and Facebook when designing the functionality of our system. When it comes to the information included in our system about fall risk awareness, we will get inspiration from Fallforebygging.no primarily because it is aimed at a Norwegian audience, the same audience as the audience for our application. 
